Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-20 cav2017/cav2017.tex
swapped sections

\subsection{Solution generalisation} 
Given the large soloution space to be searched during the inductive
synthesis phase, we parametrise the target language, which induces a
lattice of progressively more expressive languages.  This enables us
to start by attempting to synthesise a program at the lowest point on
this lattice and increase the parameters of the language until we
reach a point at which the synthesis succeeds. Whenever we manage to
synthesise a candidate solution at some lower point on the lattice, we
must apply some form of solution generalisation to obtain a full
solution (i.e. a solution in the original search space).

>>>>

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{Solution generalisation} 
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
Given the large soloution space to be searched during the inductive
synthesis phase, we parametrise the target language, which induces a
lattice of progressively more expressive languages.  This enables us
to start by attempting to synthesise a program at the lowest point on
this lattice and increase the parameters of the language until we
reach a point at which the synthesis succeeds. Whenever we manage to
synthesise a candidate solution at some lower point on the lattice, we
must apply some form of solution generalisation to obtain a full
solution (i.e. a solution in the original search space).
